% Created 2023-04-27 Thu 13:00
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Yang Huang}
\date{\textit{<2023-04-27 Thu>}}
\title{README}
\hypersetup{
 pdfauthor={Yang Huang},
 pdftitle={README},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.5.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\section{Purpose}
\label{sec:org0717de3}
Calculate two-body entropy from pair correlation function.

\section{Dependency}
\label{sec:orgce73abd}
GSL - GNU Scientific Library is required. In general, it is installed
by default in Linux operating systems. Or you can refer to \href{https://www.gnu.org/software/gsl/}{GSL
website}.

\section{Compilation}
\label{sec:org5f823e5}
Type "make" and it will generate a "pdf2s2\_v2" binary.

\section{Usage}
\label{sec:org414e2c1}
"pdf2s2\_v2 -x XDATCAR" for calculation or "pdf2s2\_v2 -h" for help page.

\subsection{Input files}
\label{sec:orga23d22c}
\begin{enumerate}
\item Mass
This file contains three rows:
\begin{itemize}
\item type of species.
\item atomic numbers.
\item atomic masses [a.u.] in atomic units.
\end{itemize}

\item Trun
This file contains in value which is the temperature of MD simulation.

\item XDATCAR
Standard output of VASP runs.

\item pdf files
Pair distribution functions. You can generate those using "pdfxdat"
command.
\end{enumerate}

\subsection{Output files}
\label{sec:orgac755e3}
\begin{enumerate}
\item pdf.??.s2
Two-body entropy as a function of integral distance of each kind of
pair in a form of
\begin{center}
\begin{tabular}{llll}
R [A] & S2(fluct) [kB] & S2(info) [kB] & S2(tot) [kB]\\
\end{tabular}
\end{center}

\item tot.s2
Total two-body entropy as a function of integral distance  a form of
\begin{center}
\begin{tabular}{llll}
R [A] & S2(fluct) [kB] & S2(info) [kB] & S2(tot) [kB]\\
\end{tabular}
\end{center}
\end{enumerate}
\end{document}